How to compute the fusion product of MV cycles in type A

### 2021-02-18 draft.tex

Now fix dominant weights $ \lambda_i \in P_+$ of size $N_i$ ($i=1,2$) and their sum $ \lambda = \lambda_1 + \lambda_2$ of size $ N = N_1 + N_2$.

% 
\begin{itemize}
    % \item Weights $\mu_i\le\lambda_i$ of size $N_i$ ($i=1,2$) 
    % \item Their sums $\mu = \sum \mu_i \le \lambda = \sum\lambda_i$ of size $N = \sum N_i$
    \item The point $L_\lambda = t^\lambda G(\cO)$ in $\Gr$ 
    \item The orbit $\Gr^\lambda = G(\cO) L_\lambda$ and its closure $ \overline{\Gr}^\lambda = \cup_{\lambda' \le \lambda} \Gr^{\lambda'}$.
    \item The family $ \overline{\Gr}^{\lambda_1, \lambda_2} \rightarrow \AA$, defined by $ \overline{\Gr}^{\lambda_1, \lambda_2} = \overline{Gr}^{\lambda_1} * \overline{Gr}^{\lambda_2}$.  By construction the fibre of $ \overline{\Gr}^{\lambda_1, \lambda_2} $ over $ s \ne 0 $ is $ \overline{\Gr}^{\lambda_1} \times \overline{\Gr}^{\lambda_2}$.  By Zhu's theorem (\jcom{need ref}), the fibre over $ 0 $ is $ \overline{\Gr}^{\lambda_1 + \lambda_2}$.
\end{itemize}
\begin{itemize}
    %The family $\overline{\Gr}_\AA^{\lambda_1,\lambda_2}\to\AA$ whose generic fibre is $\overline{\Gr}^{\lambda_1} \times \overline{\Gr}^{\lambda_2}$ and whose zero fibre is $\Gr^{\lambda}$ \acom{1. and closures? 2. can probably be described as an orbit of some group scheme} 
    \item The slice $\Gr_\mu = G_1[t^{-1}]L_\mu$ to the orbit $\Gr^\lambda$
    \item The ``slice'' $\cW_\mu = G_1\xT[t^{-1}] t^\mu G(\CC[t])$ to the ``orbit'' $\Gr_\AA^{\lambda_1,\lambda_2}$ \acom{is not presented as a family}% $(\Grbd[2])^{\lambda_1,\lambda_2}$; replaced \cW_{\mu_1,\mu_2} = by Joel's not'n & def, seemingly independent of the decomposition of \mu; modified Joel's double bracket --- still confused over where W_\mu ought to live 
\end{itemize}
The following notation leaves the realm of affine Grassmannians and probably deserves its own subsection. E.g.\ ``nilpotent cones?''
\begin{itemize}
    \item The nilpotent and semi-nilpotent cones $\cN$ and $\cN_\AA$ (of matrices with eigenvalues in $\{0\}$ and $\{0,s\} \in \AA\times\AA$ resp.) 
    \item The slice $\TT_\mu$ to the orbit $\OO_\lambda$ 
    \item The ``family of slices'' $\TT_{\mu_1,\mu_2}^{\AA}$ to the ``family of orbits'' $\OO^{\AA}_{\lambda_1,\lambda_2}$ \acom{ok to describe as such?}
\end{itemize}

>>>>

Now fix dominant weights $ \lambda_i, \mu_i \in P_+$ of size $N_i$ ($i=1,2$) and their sum $ \lambda = \lambda_1 + \lambda_2 = \mu_1 + \mu_2$ of size $ N = N_1 + N_2$.

% 
\begin{itemize}
    % \item Weights $\mu_i\le\lambda_i$ of size $N_i$ ($i=1,2$) 
    % \item Their sums $\mu = \sum \mu_i \le \lambda = \sum\lambda_i$ of size $N = \sum N_i$
    \item The point $L_\lambda = t^\lambda G(\cO)$ in $\Gr$ 
    \item The orbit $\Gr^\lambda = G(\cO) L_\lambda$ and its closure $ \overline{\Gr}^\lambda = \cup_{\lambda' \le \lambda} \Gr^{\lambda'}$.
    \item The family $ \overline{\Gr}^{\lambda_1, \lambda_2} \rightarrow \AA$, defined by $ \overline{\Gr}^{\lambda_1, \lambda_2} = \overline{Gr}^{\lambda_1} * \overline{Gr}^{\lambda_2}$.  By construction the fibre of $ \overline{\Gr}^{\lambda_1, \lambda_2} $ over $ s \ne 0 $ is $ \overline{\Gr}^{\lambda_1} \times \overline{\Gr}^{\lambda_2}$.  By Zhu's theorem (\jcom{need ref}), the fibre over $ 0 $ is $ \overline{\Gr}^{\lambda_1 + \lambda_2}$.

    \item The slice $\Gr_\mu = G_1[t^{-1}]L_\mu$ to the orbit $\Gr^\lambda$
    \item The ``slice'' $\cW_\mu = G_1\xT[t^{-1}] t^\mu G(\CC[t])$ to the ``orbit'' $\Gr_\AA^{\lambda_1,\lambda_2}$ \acom{is not presented as a family}% $(\Grbd[2])^{\lambda_1,\lambda_2}$; replaced \cW_{\mu_1,\mu_2} = by Joel's not'n & def, seemingly independent of the decomposition of \mu; modified Joel's double bracket --- still confused over where W_\mu ought to live 
\end{itemize}
The following notation leaves the realm of affine Grassmannians and probably deserves its own subsection. E.g.\ ``nilpotent cones?''
\begin{itemize}
    \item The nilpotent and semi-nilpotent cones $\cN$ and $\cN_\AA$ (of matrices with eigenvalues in $\{0\}$ and $\{0,s\} \in \AA\times\AA$ resp.) 
    \item The slice $\TT_\mu$ to the orbit $\OO_\lambda$ 
    \item The ``family of slices'' $\TT_{\mu_1,\mu_2}^{\AA}$ to the ``family of orbits'' $\OO^{\AA}_{\lambda_1,\lambda_2}$ \acom{ok to describe as such?}
\end{itemize}
